Class-based network segregation, Economic Inequality and Redistributive Preferences across societies

### 2024-04-03 paper1_jiturra_supp-material.Rmd
supplementary material

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(knitr, kableExtra, dplyr, ggplot2,sjmisc,texreg) # librerias
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = F,    # cache de los chunks,usar analisis pesados
                      out.width = '100%',
                      fig.pos= "H",     # posicion figuras H = HERE
                      fig.align = "center",
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''
```
\pagestyle{fancy}
\fancyhead[R]{\thepage}
\fancyhead[L]{Research Article Draft}

\newpage

`r if (knitr::is_latex_output()){ '\\appendix'}`

`r if (knitr::is_latex_output()){ '\\section{Appendix}'}`

@@

**Social distance**: First, the average ISEI points for each occupation of the position generator are calculated. Second, the ISEI of the respondent (R's) is subtracted from the average ISEI points of the personal network. For example, if the R's has an ISEI of 80 and the network ISEI is 50, the social distance will be 30 (80 - 50), a "upward" social distance. Another case could be 50 (R's) minus 80 (network), and the average social distance will be - 30 or "downward" social distance. In addition, When the distance is 0, the network is entirely homogeneous.

@@

@@

```{r fig5-socdistclass, echo=FALSE, fig.cap='hree-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)}
### Predicted values homo*class*GiniD ---------------------------------------
# ginid_max<- round(max(dfreg$gini_disp) ,2)
# ginid_min<- round(min(dfreg$gini_disp),2)

@@

>>>>

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")  #si falta pacman, instalar
if (!require("tinytex")) install.packages("tinytex")#si falta tinytex, instalar
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)
knitr::opts_chunk$set(warning = FALSE,  # mensaje de warning
                      message = FALSE,  # mensajes/avisos de librerias  
                      cache = F,    # cache de los chunks,usar analisis pesados
                      out.width = '100%',
                      fig.pos= "H",     # posicion figuras H = HERE
                      fig.align = "center",
                      echo = FALSE      # incluir chunk en output
                      )
options(scipen=999) # notacion cientifica
rm(list=ls())       # limpiar workspace
options(knitr.kable.NA = '') # NA en kable = ''
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
```
\pagestyle{fancy}
\fancyhead[R]{\thepage}
\fancyhead[L]{Supplementary material}

@@

@@

# Step 3: Reverse the order of the scale
reversed_values <- max(modified_values) + 0.1 - modified_values
dfreg$homclass3_V_res <- reversed_values

@@

```{r fig5-socdistclass, echo=FALSE, fig.cap='Three-way interaccion effects for Redistributive Preferences, Social Distance, Social Class and Income Inequality', fig.dim=c(12,7)}
### Predicted values homo*class*GiniD ---------------------------------------
# ginid_max<- round(max(dfreg$gini_disp) ,2)
# ginid_min<- round(min(dfreg$gini_disp),2)

@@

dfreg$homclass3_V_res <- reversed_values
